Colorism and Cosmetics: Investigating Limited Shade Ranges in the Beauty Industry in Japan and India

### 2023-04-21 outputs/paper/paper.qmd
Updated with citations

---
title: "Colorism and Cosmetics: Investigating Limited Shade Ranges in the Beauty Industry in Japan and India"
format: pdf
author: "Laura Lee-Chu"
abstract: "This research paper explores the issue of colorism in the context of the beauty industry in Japan and India. Drawing on data from an article published by The Pudding, the paper focuses on the association between the lightness and saturation of foundation shades provided by leading makeup brands in India and Japan. The findings reveal a preference for lighter shades in international brands, whereas domestic brands offer a broader spectrum of shades with warmer undertones. The study uncovers a negative correlation between the saturation and lightness of foundation shades, with Japanese foundation shades being paler and having an ashier tone, and Indian foundation shades being substantially lighter than the natural skin tone. The scarcity of foundation shades for individuals with darker skin tones can lead to their marginalization and exclusion, perpetuating the issue of colorism in the beauty industry."
date: today
date-format: long
editor: visual
toc: TRUE
number-sections: TRUE
bibliography: references.bib
thanks: "Code and data supporting this analysis is available at: "
---

@@

#### Preamble ####
# Title:
# Author: Laura Lee-Chu
# Email: 
# Date: 16 March 2023

>>>>

---
title: "Colorism and Cosmetics: Investigating Limited Shade Ranges in the Beauty Industry in Japan and India"
format: pdf
author: "Laura Lee-Chu"
abstract: "This research paper explores the issue of colorism in the context of the beauty industry in Japan and India. Drawing on data from an article published by The Pudding, the paper focuses on the association between the lightness and saturation of foundation shades provided by leading makeup brands in India and Japan. The findings reveal a preference for lighter shades in international brands, whereas domestic brands offer a broader spectrum of shades with warmer undertones. The study uncovers a negative correlation between the saturation and lightness of foundation shades, with Japanese foundation shades being paler and having an ashier tone, and Indian foundation shades being substantially lighter than the natural skin tone. The scarcity of foundation shades for individuals with darker skin tones can lead to their marginalization and exclusion, perpetuating the issue of colorism in the beauty industry."
date: today
date-format: long
editor: visual
toc: TRUE
number-sections: TRUE
bibliography: references.bib
thanks: "Code and data supporting this analysis is available at: https://github.com/lauraleechu/shades"
---

@@
